\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-29 Report/project_report.tex
Added some plots to the report. Restructured the folders
Lovely plots
Added minor grid lines
Gridlines yo
Figure cleanup

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the error in the state.
Since the error in the feature positions \textit{is} correlated to the error in the state, $\Vec{r}^{(j)}$ cannot be used in the EKF directly. [TALK HERE ABOUT WHAT HAPPENS IF YOU LEAVE IT IN]

@@

>>>>

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the error in the state.
Since the error in the feature positions \textit{is} correlated to the error in the state, $\Vec{r}^{(j)}$ cannot be used in the EKF directly.
Figure \ref{fig:nullspace} shows the effect of attempting to use this error directly in the EKF.
The correlation between the measurement error on the state causes the filter to behave very poorly after a small number of time steps.

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/NST_trans}
        \label{fig:nullspace:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/NST_rot}
        \label{fig:nullspace:rot_err}
    }

    \caption{Effect of nullspace projection on MSCKF performance}
    \label{fig:nullspace}
\end{figure}

@@

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/Comparison-Trans-Error}
        \label{fig:comp_1:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/Comparison-Rot-Error}
        \label{fig:comp_1:rot_err}
    }

    \caption{MSCKF vs. SWF}
    \label{fig:comp_1}
\end{figure}
